### 2018-04-30 paper/message-passing-design.tex
up

Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function 
(\cref{SPORRecv}).

>>>>

Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function 
(\cref{SPORRecv}).
